Verifying Demonstrations

### 2018-11-30 paper/protocol.tex
Puts long math on own line

We now present \CROCUS, a protocol for privately verifiable crowd counts.
The protocol consists of three phases:
before the protest, with the setup and registration steps (\cref{ProtocolSetup}),
during the protest, with the creation, join, participation, and submission steps (\cref{ProtocolDuring})
and after the protest, with the verification step (in
\cref{ProtocolVerification}). Note that some of the figures with
protocol minutae from related work are in the
appendix.

Several entities are involved in our protocol.
First, a \emph{certificate authority} (\ac{CA}) is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be done by a centralized authority, such as a nation state with, 
  \eg, passports; or a decentralized authority, as in the case of a a 
  collective authority~\cite{collective-signing} powered by 
  proof-of-personhood~\cite{proof-of-personhood}.
}.
The \ac{CA} is only involved in the setup phase.
Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forwards it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

@@

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}

During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

@@

The protester sends \(\pid\) to the witness.
Then they run the protocol \(\Proto{\ACproveSig[\spk, k, r, 
    \sigma]}{\ACverifySig[\spk, \ssk]}\) (see \cref{ACacAlg}).
Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
If the protocol succeeds, the witness will compute \(\wid \gets 
  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.

@@

Then the set of all valid proof shares for a protester \(j\) constitutes its participation proof \(\pi_{j}\), as in \cref{DefParticipationProof},
and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst)\), as in \cref{DefParticipationProof}.
Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by the same \cref{DefParticipationProof}.

@@

In the case of trusted witnesses, each such trusted witness must
publish or otherwise inform the 
verifier of which proof shares she has signed, \eg by giving a list 
of all such proof shares or digitally signing each proof share\footnote{
 To achieve witness privacy in this situation, one could employ a group or 
 ring signature scheme for all trusted witnesses.
 Then one learns that at least one trusted witness must have been there.
}.

Note that anyone who does the counting can choose the eligibility
criteria (time interval, location, number of regular or trusted
witnesses, who is considered to be a trusted witness) for their count
and as long as these are published along with the result, anyone can
verify the correctness under those criteria.

>>>>

We now present \CROCUS, a protocol for privately verifiable crowd counts.
The protocol consists of three phases:
before the protest, with the setup and registration steps (\cref{ProtocolSetup});
during the protest, with the creation, join, participation, and submission 
steps (\cref{ProtocolDuring});
and after the protest, with the verification step (in
\cref{ProtocolVerification}). Note that some of the figures with
protocol minutiae from related work are in~\cref{anon-cred-figures}.

Several entities are involved in our protocol.
First, a \emph{certificate authority} (\ac{CA}) is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key
%\footnote{%
%  This can be done by a centralized authority, such as a nation state with, 
%  \eg, passports; or a decentralized authority, as in the case of a a 
%  collective authority~\cite{collective-signing} powered by 
%  proof-of-personhood~\cite{proof-of-personhood}.
%}.
For simplicity, we assume that the \ac{CA} is a trusted third-party, but its role is only important to prevent Sybil attacks, so in practice we only need the \ac{CA} to not be aligned with the protesters. For instance, the role of the \ac{CA} can be assumed by a centralized authority, such as a nation state with, 
\eg, passports, and that would not impact the trust of a participation count for a protest \emph{against} this state. However, any pro-state demonstration in that context would be subject to Sybils. Another possibility would be to use a decentralized authority, as in the case of a 
collective authority~\cite{collective-signing} powered by 
proof-of-personhood~\cite{proof-of-personhood}.
The \ac{CA} is only involved in the setup phase.

Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forwards it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

@@

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

@@

The protester sends \(\pid\) to the witness.
Then they run the protocol \[
  \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
\] (see \cref{ACacAlg}).
Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
If the protocol succeeds, the witness will compute \(\wid \gets 
  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.

@@

Then the set of all valid proof shares for a protester \(j\) constitutes its participation proof \(\pi_{j}\), as in \cref{DefParticipationProof},
and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst\), as in \cref{DefParticipationCount}.
Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by the same \cref{DefParticipationCount}.

@@

In the case of trusted witnesses, each such trusted witness must
publish or otherwise inform the 
verifier of which proof shares they have signed, \eg by giving a list 
of all such proof shares or digitally signing each proof share\footnote{
 To achieve witness privacy in this situation, one could employ a group or 
 ring signature scheme for all trusted witnesses.
 Then one learns that at least one trusted witness must have been there.
}.

Note that, thanks to the \((\str,\theta)\)-eligibility criterion (\cref{DefParticipationCount}), the method of counting is extremely generic, and each verifier can make an independent choice to regulate their trust in the final result, based on their initial trust in the witnesses. In other words, anyone who does the counting can choose the eligibility
criteria (time interval, location, number of regular or trusted
witnesses, who is considered to be a trusted witness) for their own count
and as long as these are published along with the result, anyone can
verify the correctness of the count under those criteria, and potentially question the validity of this choice. Biased or partisan verifiers may be tempted to make extreme choices, but they will have to publish those choices and lose credibility. Reasonable verifiers on the other hand will try to find a good middle-ground that counts all legitimate protesters while being resistant to isolated malicious agents.
